Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-07-04 analysis/paper/paper.Rmd
Add grDevices to libraries in Rmd files

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "tidyr",
  "tools"
)

@@

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = c("postscript"),
  out.width = "100%",
  comment = "#>",
  dev = "cairo_pdf",
  cache = FALSE
)

>>>>

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "tidyr",
  "tools"
)

@@

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  out.width = "100%",
  comment = "#>",
  dev = "cairo_ps",
  cache = FALSE
)

### 2022-07-04 analysis/supplementary materials/supplementary materials.Rmd
Add grDevices to libraries in Rmd files

library("Reproducibility.in.Plant.Pathology")
packages <- c(
  "tidyverse",
  "bayesplot",
  "bayestestR",
  "brms",
  "extrafont",
  "flextable",
  "ggpubr",
  "here",
  "knitr",
  "officer",
  "pander",
  "parameters",
  "posterior",
  "report",
  "tools"
)

@@

>>>>

library("Reproducibility.in.Plant.Pathology")
packages <- c(
  "tidyverse",
  "bayesplot",
  "bayestestR",
  "brms",
  "extrafont",
  "flextable",
  "grDevices",
  "ggpubr",
  "here",
  "knitr",
  "officer",
  "pander",
  "parameters",
  "posterior",
  "report",
  "tools"
)

@@

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = "cairo_ps"
)
